Leadership across cultures and contexts: an exploratory analysis

### 2020-04-25 leadership_across_cultures_contexts.Rmd
Tweaked caption of variablesupport.

```{r varsupport, fig.width=15, fig.height=15, fig.cap="Support for each coded variable of leader functions (top) and qualities (bottom). Blue circles: percent of text records with evidence of support (95% CI computed with a binomial mixed effects models with random intercept for author nested within culture). Red triangles: percent of cultures with evidence of support (95% CI computed with a cluster bootstrap)."}
ggsave(file="Figures/variablesupport.pdf", plot_func_qual)
plot_func_qual
```

>>>>

```{r varsupport, fig.width=15, fig.height=15, fig.cap="Evidence for each coded variable of leader functions (top) and qualities (bottom). Red: percent of text records with evidence of support (95% CI computed with a binomial mixed effects models with random intercept for author nested within culture). Purple: percent of cultures with evidence of support (95% CI computed with a cluster bootstrap)."}
ggsave(file="Figures/variablesupport.pdf", plot_func_qual)
plot_func_qual
```
